Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-01-18 SupportingInformation.Rmd
test run with neg beta ar1 model

```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=3)
op<-par(mfrow=c(1,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise copula,", "population copula,",  "Gof test : p-value(CvM),", "Gof test : p-value(KS)"), col = c("red","blue", "magenta", "green2"),
       cex = 0.9, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0),
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------

pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=3)
op<-par(mfrow=c(1,2))

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
legend("top", c("noise copula,", "population copula,",  "Gof test : p-value(CvM),", "Gof test : p-value(KS)"), col = c("red","blue", "magenta", "green2"),
       cex = 0.9, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0),
       bty = "n") 
par(op)
dev.off()
```

```{r cause4copula_stat, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
resloc<-"./Results/Cause4copula_results/"
if (!dir.exists(paste(resloc,"Cause4copula_stat_results",sep=""))){
  dir.create(paste(resloc,"Cause4copula_stat_results",sep=""))
}
resloc<-paste(resloc,"Cause4copula_stat_results/",sep="")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc)                
```

\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Spearman_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Kendall_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pearson_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Corl_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Coru_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Corl-Coru_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pu_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl-Pu_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2l_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u-D2l_vs_Spearman's Rho.pdf}
\caption[Comparing correlations and non-parametric statistic between upper tail dependent noise-copula (\textbf{Survival Clayton}) and population copula for different \textbf{Spearman's Rho}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from upper tail dependent \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant \textbf{Spearman's Rho} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. \label{fig_Cause4copula_SC_spear}}
\end{center}
\end{figure}

>>>>

```{r cause4copula_pGOF_500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
#source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
#pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_500.pdf", width=8, height=3)
#op<-par(mfrow=c(1,2))

#Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=500,BS=1000)

#Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=500,BS=1000)

@@

#op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
#plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
#legend("top", c("noise copula,", "population copula,",  "Gof test : p-value(CvM),", "Gof test : p-value(KS)"), col = c("red","blue", #"magenta", "green2"),
#       cex = 0.9, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0),
#       bty = "n") 
#par(op)
#dev.off()
```

```{r cause4copula_pGOF_2500, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
#source("Cause4copula.R")
#-----------------
#set.seed(seed)
#---------------------------------------

#pdf("./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf", width=8, height=3)
#op<-par(mfrow=c(1,2))

#Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "spearman",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="spearman",num_keep_last=2500,BS=1000)

#Plotter_Cause4copula_GOF(N=5000,fcode=3,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=13,method="kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=4,method = "kendall",num_keep_last=2500,BS=1000)
#Plotter_Cause4copula_GOF(N=5000,fcode=14,method="kendall",num_keep_last=2500,BS=1000)

#op<-par(fig = c(0, 1, 0, 1), oma = c(0, 0, 0, 0), mar = c(0, 1, 0, 0), new = TRUE)
#plot(0, 0, type = "n", bty = "n", xaxt = "n", yaxt = "n")
#legend("top", c("noise copula,", "population copula,",  "Gof test : p-value(CvM),", "Gof test : p-value(KS)"), col = c("red","blue", #"magenta", "green2"),
#       cex = 0.9, pch = c(2, 6, 16, 16), xpd = TRUE, horiz = TRUE, inset = c(0,0),
#       bty = "n") 
#par(op)
#dev.off()
```

```{r cause4copula_stat_clayton_ar1_posbeta, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
#source("Cause4copula.R")
#-----------------
#set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
#resloc<-"./Results/Cause4copula_results/"
#model<-"ar1"
#params<-c(0.5) # this parameter is beta in ar1 model
#tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,sep="")

#if (!dir.exists(tempo)){
#  dir.create(tempo)
#}

#resloc<-paste(tempo,"/",sep="")

# for clayton with spearman and kendall method
#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")

#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")

# for survival clayton with spearman and kendall method
#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")

#Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
#                          params=params,p0=c(0,0),model="ar1")
```

```{r cause4copula_stat_clayton_ar1_negbeta, echo=F, results="hide", cache=T, cache.extra=list(seed,mtime("Cause4copula.R"),mtime("CopulaFunctions_flexible.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("Cause4copula.R")
#-----------------
set.seed(seed)
#---------------------------------------
# This chunk stores results for ar1 model 
resloc<-"./Results/Cause4copula_results/"
model<-"ar1"
params<-c(-0.5) # this parameter is beta in ar1 model
tempo<-paste(resloc,"Cause4copula_stat_results_",model,"_beta_",params,sep="")

if (!dir.exists(tempo)){
  dir.create(tempo)
}

resloc<-paste(tempo,"/",sep="")

# for clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=3,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

# for survival clayton with spearman and kendall method
Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="spearman",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")

Plotter_Cause4copula_stat(N=5000,numsim=50,fcode=13,method="kendall",lb=0,ub=0.1,num_keep_last=500,resloc=resloc,
                          params=params,p0=c(0,0),model="ar1")               
```

<!--
\begin{figure}[!h]
\begin{center}
\includegraphics[width=16 cm]{./Results/Cause4copula_results/compare_params_pGOF_num_keep_last_2500.pdf}
\caption[Comparing noise-copula parameters and estimated population copula parameters with $2500$ sampling points]{Results of comparison between the parameters of environmental noise generated from a specific family of copula and estimated sample parameter (with some standard error) of the affected populations (Initially 5000 points are generated but we kept last \textbf{2500} points for both noise and population data for comparison). p-values $> 0.05$ (above horizontal dashed line) indicate good fit of population copula with same noise cpoula family. \label{fig_Cause4copula_params_GOF_2500}}
\end{center}
\end{figure}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Spearman_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Kendall_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Pearson_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Corl_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Clayton_Coru_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Corl-Coru_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pu_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_Pl-Pu_vs_Spearman's Rho.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2l_vs_Spearman's Rho.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results/Survival Clayton_D2u-D2l_vs_Spearman's Rho.pdf}
\caption[Comparing correlations and non-parametric statistic between upper tail dependent noise-copula (\textbf{Survival Clayton}) and population copula for different \textbf{Spearman's Rho}]{Results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from upper tail dependent \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant \textbf{Spearman's Rho} values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. \label{fig_Cause4copula_SC_spear}}
\end{center}
\end{figure}
-->
